Choosing TTC Subway Service Provides the Most Time Stability during Weekday Rush-Hours

### 2024-09-24 outputs/paper/paper.qmd
solved rendered figure title overlapping issue in section 3.2

# Generate the bar plot
sum_graph <- ggplot(total_delay_time, aes(x = service_type, y = sum_delay_time/60, fill = service_type)) +
  geom_bar(stat = "identity") + 
  # Add labels for total hours
  geom_text(aes(label = paste0(round(sum_delay_time / 60, 2), "hrs")), 
            vjust = 1, color = "black", size = 1.5, lineheight = 0.8, position = position_stack(vjust = 0.6)) +  
  labs(title = "Total Weekday Delay (hrs)", 
       x = "Service Type", y = "Total Delayed (hrs)", fill = "Service Type") +  # Label the axes
  theme_minimal() +
  theme(legend.position = "none", axis.text.x = element_text(size = 8))

avg_graph <- ggplot(avg_delay_time, aes(x = service_type, y = mean_delay_time, fill = service_type)) +
  geom_bar(stat = "identity") + 
  # Add labels for total hours
  geom_text(aes(label = paste0(round(mean_delay_time, 1), " mins")), 
            vjust = 1, color = "black", size = 2, position = position_stack(vjust = 0.6)) +  
  labs(title = "Average Weekday Delay (min)", 
       x = "Service Type", y = "Average Delay Time (min)", fill = "Service Type") +  # Label the axes
  theme_minimal() +
  theme(axis.text.x = element_text(size = 8))

>>>>

# Generate the bar plot
sum_graph <- ggplot(total_delay_time, aes(x = service_type, y = sum_delay_time/60, fill = service_type)) +
  geom_bar(stat = "identity") + 
  # Add labels for total hours
  geom_text(aes(label = paste0(round(sum_delay_time / 60, 2), "hrs")), 
            vjust = 1, color = "black", size = 1.6, lineheight = 0.8, position = position_stack(vjust = 0.6)) +  
  labs(title = "Total Weekday Delay (hrs)", 
       x = "Service Type", y = "Total Delayed (hrs)", fill = "Service Type") +  # Label the axes
  theme_minimal() +
  theme(legend.position = "none", axis.text.x = element_text(size = 8), 
        plot.title = element_text(size = 11))

avg_graph <- ggplot(avg_delay_time, aes(x = service_type, y = mean_delay_time, fill = service_type)) +
  geom_bar(stat = "identity") + 
  # Add labels for total hours
  geom_text(aes(label = paste0(round(mean_delay_time, 1), "mins")), 
            vjust = 1, color = "black", size = 2, position = position_stack(vjust = 0.6)) +  
  labs(title = "Average Weekday Delay (min)", 
       x = "Service Type", y = "Average Delay Time (min)", fill = "Service Type") +  # Label the axes
  theme_minimal() +
  theme(axis.text.x = element_text(size = 8), 
        plot.title = element_text(size = 11))
